Hydra Battles and Cie

### 2021-03-07 doc/chapter-primrec.tex
minor corrections
simplification of a proof

@@

  Fact Ack_majorized : majorized (Ack: naryFunc 2)  Ack.
 \end{Coqsrc}

 In order to share the variable \texttt{n}, let us open a section.

\begin{Coqsrc}
  Section Contrad.
    Variable n: nat.
    Hypothesis  Hn: forall x y,  Ack x y <= Ack n (max x  y).
\end{Coqsrc}

Firs, we get rid of the cases $n=0$ and $n=1$, thus we can rewrite
(\texttt{max 2 n}) into \texttt{n}.

  \begin{Coqsrc}
    Remark R01: n <> 0.

    Remark R02: n <> 1.

    Remark R03: max 2 n = n.
\end{Coqsrc}

Please keep in mind that \texttt{(2 * n + 3)} can be safely replaced with 
\texttt{(Ack 2 n)}.

\begin{Coqsrc}
    Remark R04: Ack n (2 * n + 3) = Ack n (Ack 2 n).

    Remark R05: Ack n (2 * n + 3) <= Ack (n + 2) n.
\end{Coqsrc}

 By hypothesis \texttt{Hn}, the following inequality holds.

 \begin{Coqsrc}
    Remark R06: Ack (n + 2) n <= Ack n (n + 2).
 \end{Coqsrc}

By monotony of the Ackerman function, we get:

\begin{Coqsrc}
    Remark R07: Ack n (n + 2) < Ack n (2 * n + 3).
\end{Coqsrc}

which contradicts \texttt{R05}.

\begin{Coqsrc}
    Lemma contrad : False.

  End Contrad.

  Lemma Ack_not_PR : False.

>>>>

Since The Ackermann function is strictly monotonous in its first argument\footnote{almost always\dots}, we may replace the large inequality with a strict one.

\vspace{4pt}
\noindent
\emph{From \href{../theories/html/hydras.MoreAck.Ack.html}{MoreAck.Ack}.}

\begin{Coqsrc}
Lemma Ack_strict_mono_l : forall n m p, n < m ->
                                        Ack n (S p) < Ack m (S p).
\end{Coqsrc}

\vspace{4pt}
\noindent
\emph{From \href{../theories/html/hydras.MoreAck.AcknotPR.html}{MoreAck.AckNotPR}.}

\begin{Coqsrc}
Lemma majorPR2_strict (f: naryFunc 2)(Hf : isPR 2 f):
    exists (n:nat),
    forall x y, 2 <= x -> 2 <= y -> f x y < Ack n (max x  y).
\end{Coqsrc}

@@

  Lemma Ack_not_PR : False.
  Proof.
    destruct (majorPR2_strict Ack HAck) as [m Hm];
    pose (X := max 2 m); specialize (Hm X X).
    rewrite max_idempotent in Hm; 
    assert (Ack m X <= Ack X X) by (apply Ack_mono_l; lia).
    lia.
  Qed.
